### 2019-02-01 introduction.tex
fixing LTI

The goal of examining the arrival runway occupancy times and the landing time intervals is to determine whether the implementation of the RECAT-EU scheme at BIKF under certain conditions, would affect the throughput of the airfield. Additionally the analysis could indicate whether the limiting factor is the runway occupancy time or the separation requirement. The proposed transition by EUROCONTROL from ICAO WTS to RECAT-EU scheme suggests reduced distance separation for certain aircraft pairs (Table~\ref{tab:delta_distance_wtc2recat}). The reduction is reveled by shifting the wake turbulence separation minima for arrival pairs, creating the potential for reduced spacing between aircraft, hence reducing the time interval between landings (LTI) and facilitating increased throughput capacity of the runways.

>>>>

The goal of examining the arrival runway occupancy times and the landing time intervals is to determine whether the implementation of the RECAT-EU scheme at BIKF under certain conditions, would affect the throughput of the airfield. Additionally the analysis could indicate whether the limiting factor is the runway occupancy time or the separation requirement. The proposed transition by EUROCONTROL from ICAO WTS to RECAT-EU scheme suggests reduced distance separation for certain aircraft pairs (Table~\ref{tab:delta_distance_wtc2recat}). This reduction, revealed by shifting the wake turbulence separation minima for arrival pairs, creates potential for reduced spacing between aircraft, hence reducing the time interval between landings (LTI) and facilitating increased throughput capacity of the runways.
